---
title: "Practicum"
author: "Jiaqing Ge"
date: "2/19/2020"
output:
  html_document: 
      keep_md: true
      always_allow_html: true
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Packages needed
```{r, message=FALSE,warning=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(wordcloud)
library(plotly)
library(ggthemes)
library(gapminder)
library(scales)
library(usmap)
library(tidycensus)
library(lubridate)
library(TTR)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(tidytext)
library(stringr)
```

# 2. Import data
```
complaints <- read.csv('complaints.csv',stringsAsFactors = FALSE)
saveRDS(complaints, file = "complaints_raw.rds") # This line change complaints.csv to dataset that works with R. 
complaints_raw <- readRDS("complaints_raw.rds")
```

# 3. Randomly draw 5000 rows of data to do the analysis.
```
subset <- complaints_raw[sample(nrow(complaints_raw), size = 5000, replace = FALSE),]
saveRDS(subset, file = "complaints_sub.rds")
```

# 4. take a look at it.
```{r}
complaints_test <- readRDS('complaints_sub.rds')
head(complaints_test,100) %>%
  View()
glimpse(complaints_test)
```

# 5. Change date received to year-month-day
```{r}
complaints_test <- complaints_test %>%
  mutate(year = as.integer(substr(Date.received, start = 1, stop = 4))) %>%
  mutate(month = as.integer(substr(Date.received, start = 6, stop = 7))) %>%
  mutate(day = as.integer(substr(Date.received, start =9 , stop = 10)))
complaints_test$Date.received <- ymd(complaints_test$Date.received)
str(complaints_test)
```

# 6. Ploting of the number of complaints throughout the year
### Ploting overall number of complaints throughout the year
```{r,warning=FALSE, message=FALSE}
p <- complaints_test %>% 
  mutate(date = as.POSIXct(paste(month , day , sep = "." )  , format = "%m.%d" )) %>%
  group_by(date) %>%
  summarise(number_of_complaints = n()) %>%
  ggplot(aes(x = date, y = number_of_complaints))+ geom_point()+ylab("Number of complaints")+
  theme_economist()+
  scale_x_datetime(labels=  date_format("%b-%d"),date_breaks = '1 month')+
  geom_smooth(lwd=1, se=FALSE,color = 'red')+
  geom_line(aes(x=date, y=SMA(number_of_complaints,10), color = 'red'))+ 
  theme(legend.position="none")+
  ggtitle("Overall number of complaints throughout a year")
ggplotly(p)
```

In this graph, I plot a graph showing the number of complaints through out a year to see whether there are more complaints in certain months or day. We can see from the graph that there are a few outliars that are very low appears at the beginning of the month. On Jan-01, Mar-01, Jul-01 and Sep-01, the number of complaints drops significantly. 

### Ploting number of complaints of certain complany through out the year through out the year
```{r,warning=FALSE, message=FALSE}
simpleCap <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), substring(s, 2),
      sep="", collapse=" ")
} # This line change the format of company names
complaints_pattern_company <- function(x){ 
p_ <-  complaints_test %>% 
  filter(Company == x)  %>%
  mutate(date = as.POSIXct(paste(month , day , sep = "." )  , format = "%m.%d" )) %>%
  group_by(date) %>%
  summarise(number_of_complaints = n()) %>%
  ggplot(aes(x = date, y = number_of_complaints))+ geom_point()+ylab("Number of complaints")+
  theme_economist()+
  scale_x_datetime(labels=  date_format("%b-%d"),date_breaks = '1 month')+
  geom_smooth(lwd=1, se=FALSE,color = 'red')+
  geom_line(aes(x=date, y=SMA(number_of_complaints,10), color = 'red'))+ 
  theme(legend.position="none")+
  ggtitle(paste("Number of Complaints throughout a Year:",simpleCap(tolower(x)), sep = ' '))
ggplotly(p_)}
complaints_pattern_company('BANK OF AMERICA, NATIONAL ASSOCIATION')
```

### Ploting number of complaints of certain product through out the year through out the year
```{r, message=F}
complaints_pattern_product <- function(x){ 
p_ <-  complaints_test %>% 
  filter(Product == x)  %>%
  mutate(date = as.POSIXct(paste(month , day , sep = "." )  , format = "%m.%d" )) %>%
  group_by(date) %>%
  summarise(number_of_complaints = n()) %>%
  ggplot(aes(x = date, y = number_of_complaints))+ geom_point()+ylab("Number of complaints")+
  theme_economist()+
  scale_x_datetime(labels=  date_format("%b-%d"),date_breaks = '1 month')+
  geom_smooth(lwd=1, se=FALSE,color = 'red')+
  geom_line(aes(x=date, y=SMA(number_of_complaints,10), color = 'red'))+ 
  theme(legend.position="none")+
  ggtitle(paste("Number of Complaints throughout a Year:",simpleCap(tolower(x)), sep = ' '))
ggplotly(p_)}
complaints_pattern_product('Debt collection')
```

### Ploting companies with highest number of complaints
```{r,fig.height = 5, fig.width = 15}
Top_10_comanies <- complaints_test %>%
  group_by(Company) %>%
  summarise(number_of_complaints = n())%>%
  arrange(desc(number_of_complaints))%>%
  head(10)%>%
  select(Company) # This line select the companies with most complaints
p_1 <- complaints_test %>%
  filter(Company %in% Top_10_comanies$Company) %>%
  group_by(Company,Product)%>%
  summarise(number_of_complaints = n())%>%
  ungroup()%>%
  mutate(Company = factor(Company, levels=Top_10_comanies$Company))%>%
  ggplot(aes(fill=Product, y=number_of_complaints, x=Company)) + 
  geom_bar(position="stack", stat="identity")+ylab('Nunber of Complaints by Company')+coord_flip()+theme(legend.position="right")+guides(fill=guide_legend(nrow=15))
ggplotly(p_1,width = 1500, height = 500, type = 'bar')
```

```{r,height = 5, fig.width = 10}
share_of_products_ <- complaints_test %>%
  group_by(Product) %>%
  summarize(count = n()) %>%
  plot_ly(labels = ~Product, values = ~count,width = 1200, height = 500) %>%
  add_pie(hole = 0.6) %>%
  layout(title = "Share of Products",  showlegend = T,
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),legend = list(x = 100, y = 0.5))
share_of_products_
```

### Ploting products with highest number of complaints
```{r,fig.height = 5, fig.width = 10}
Top_10_product <- complaints_test %>%
  group_by(Product) %>%
  summarise(number_of_complaints = n())%>%
  arrange(desc(number_of_complaints))%>%
  head(10)%>%
  select(Product) # This line select the companies with most complaints
p_2 <- complaints_test %>%
  filter(Product %in% Top_10_product$Product) %>%
  group_by(Product,Submitted.via)%>%
  summarise(number_of_complaints = n())%>%
  ungroup()%>%
  mutate(Product = factor(Product, levels=Top_10_product$Product))%>%
  ggplot(aes(fill=Submitted.via, y=number_of_complaints, x=Product)) + 
  geom_bar(position="stack", stat="identity")+ylab('Nunber of Complaints by Product')+coord_flip()+theme(legend.position="bottom")
ggplotly(p_2,width = 1200, height = 500, type = 'bar')
```

# 7. Mapping the complaints in different states

## The overall complaints number accross U.S.
```{r,message=F, warning=FALSE}
census_api_key(Sys.getenv('CENSUS_API_KEY'))
state_pop <- get_acs(
  geography = "state",
  variables = "B01003_001",
  year = 2018,
  survey = "acs5"
  )%>%
  mutate(fips = fips(NAME))%>%
  mutate(State = state.abb[match(NAME,state.name)])%>%
  select(NAME,estimate,fips,State)%>%
  mutate(state = NAME)%>%
  mutate(state_population = estimate)%>%
  select(-NAME,-estimate)
state_pop <- as.data.frame(state_pop)
state_complaint <- complaints_test %>%
  group_by(State) %>%
  summarise(number_of_complaints = n())%>%
  ungroup()
state_complaint <- left_join(state_complaint,state_pop)
state_complaint <- state_complaint%>%
  mutate(state_adjusted_complaints = number_of_complaints/state_population*100000)
state_complaint <- as.data.frame(state_complaint)%>%
  filter(!is.na(state))
plot_usmap(data = state_complaint, values = "state_adjusted_complaints", color = "red")+scale_fill_continuous(
    low = "white", high = "red", name = "Complaints by State (adjusted by population)", label = scales::comma) + theme(legend.position = "right")
```

## complaints number accross U.S.
```{r,message=F}
company_complaints_mapping <- function(x){
state_complaint <- complaints_test %>%
  filter(Company == x) %>%
  group_by(State) %>%
  summarise(number_of_complaints = n())%>%
  ungroup()
state_complaint <- left_join(state_complaint,state_pop)
state_complaint <- state_complaint%>%
  mutate(state_adjusted_complaints = number_of_complaints/state_population*1000000)
state_complaint <- as.data.frame(state_complaint)%>%
  filter(!is.na(state))
plot_usmap(data = state_complaint, values = "state_adjusted_complaints", color = "orange")+scale_fill_continuous(
    low = "white", high = "orange", name = "Complaints by State (adjusted by population)", label = scales::comma) + theme(legend.position = "right")}
company_complaints_mapping('BANK OF AMERICA, NATIONAL ASSOCIATION')
```

# 8. Text mining and word cloud for complaints involving monetary relief or not.

## set up corpus for narrative complaints
```{r}
complaints_narrative_corp <- complaints_test %>%
  select(Company.response.to.consumer,Consumer.complaint.narrative)%>%
  filter(!is.na(Consumer.complaint.narrative))%>%
  filter(Consumer.complaint.narrative != '')%>%
  group_by(Company.response.to.consumer)%>%
  summarise(narrative = paste0(Consumer.complaint.narrative,collapse = " "))%>%
  ungroup()%>%
  unnest_tokens(word, narrative) %>%
  count(Company.response.to.consumer,word, sort = TRUE)
```

## data cleaning
```{r, message=F}
complaints_narrative_corp <- complaints_narrative_corp %>%
  filter(word %in% stopwords("english") == FALSE)%>%
  filter(word %in% c("xxxx", "xxxxxxxx", "xx") == FALSE)%>%
  mutate(word = tolower(word))%>%
  filter(str_detect(word, "^[0-9]")==FALSE)%>%
  filter(str_detect(word,'[[:punct:] ]+')==FALSE)%>%
  filter(str_detect(word,' ')==FALSE)
```

## calculate number of words of each issue
```{r, message=F}
total_words <- complaints_narrative_corp %>% 
  group_by(Company.response.to.consumer) %>%
  summarize(total = sum(n))
complaints_narrative_corp <- left_join(complaints_narrative_corp, total_words)
```

```{r}
complaints_narrative_corp <- complaints_narrative_corp %>%
  bind_tf_idf(word, Company.response.to.consumer, n)
```

```{r}
complaints_narrative_corp <- complaints_narrative_corp %>%
  select(-total) %>%
  arrange(desc(tf_idf))
str(complaints_narrative_corp)
```

```{r,fig.height = 10, fig.width = 10}
p_5 <- complaints_narrative_corp %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(Company.response.to.consumer) %>% 
  top_n(10) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = Company.response.to.consumer)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~Company.response.to.consumer, ncol = 2, scales = "free") +
  coord_flip()
ggplotly(p_5,width = 1000, height = 1000, type = 'bar')
```


## word cloud with tf_idf
```{r,warning=FALSE}
complaints_narrative_corp <- complaints_narrative_corp %>%
    filter(Company.response.to.consumer == 'Closed with monetary relief')
wordcloud(words = complaints_narrative_corp$word, freq = complaints_narrative_corp$tf_idf,
    max.words=200, random.order=FALSE, rot.per=0.35, 
    colors=brewer.pal(8, "Dark2"))
```

## word cloud with frequency of words
```{r,warning=FALSE}
wordcloud(words = complaints_narrative_corp$word, freq = complaints_narrative_corp$n,
    max.words=200, random.order=FALSE, rot.per=0.35, 
    colors=brewer.pal(8, "Dark2"))
```

## repeat all of that using bigram
```{r}
complaints_narrative_corp_2 <- complaints_test %>%
  select(Company.response.to.consumer,Consumer.complaint.narrative)%>%
  filter(!is.na(Consumer.complaint.narrative))%>%
  filter(Consumer.complaint.narrative != '')%>%
  group_by(Company.response.to.consumer)%>%
  summarise(narrative = paste0(Consumer.complaint.narrative,collapse = " "))%>%
  ungroup()%>%
  unnest_tokens(word, narrative)%>%
  filter(word %in% stopwords("english") == FALSE)%>%
  filter(word %in% c("xxxx", "xxxxxxxx", "xx") == FALSE)%>%
  mutate(word = tolower(word))%>%
  filter(str_detect(word, "^[0-9]")==FALSE)%>%
  filter(str_detect(word,'[[:punct:] ]+')==FALSE)%>%
  filter(str_detect(word,' ')==FALSE)%>%
  group_by(Company.response.to.consumer)%>%
  summarise(narrative = paste0(word,collapse = " "))%>%
  unnest_tokens(bigrams, narrative, token = "ngrams", n = 2)%>%
  count(Company.response.to.consumer,bigrams, sort = TRUE)
```

```{r, message=F}
total_words_2 <- complaints_narrative_corp_2 %>% 
  group_by(Company.response.to.consumer) %>%
  summarize(total = sum(n))
complaints_narrative_corp_2 <- left_join(complaints_narrative_corp_2, total_words_2)
```

```{r}
complaints_narrative_corp_2 <- complaints_narrative_corp_2 %>%
  bind_tf_idf(bigrams, Company.response.to.consumer, n)
```

```{r}
complaints_narrative_corp_2 <- complaints_narrative_corp_2 %>%
  select(-total) %>%
  arrange(desc(tf_idf))
```

```{r,fig.height = 10, fig.width = 10}
p_5 <- complaints_narrative_corp_2 %>%
  arrange(desc(tf_idf)) %>%
  mutate(bigrams = factor(bigrams, levels = rev(unique(bigrams)))) %>%
  group_by(Company.response.to.consumer) %>% 
  top_n(10) %>% 
  ungroup() %>%
  ggplot(aes(bigrams, tf_idf, fill = Company.response.to.consumer)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~Company.response.to.consumer, ncol = 2, scales = "free") +
  coord_flip()
ggplotly(p_5,width = 1000, height = 1000, type = 'bar')
```

## word cloud with tf_idf
```{r,warning=FALSE}
complaints_narrative_corp_2 <- complaints_narrative_corp_2 %>%
    filter(Company.response.to.consumer == 'Closed with monetary relief')
wordcloud(words = complaints_narrative_corp_2$bigrams, freq = complaints_narrative_corp_2$tf_idf,
    max.words=200, random.order=FALSE, rot.per=0.35, 
    colors=brewer.pal(8, "Dark2"))
```

## word cloud with frequency of words
```{r,warning=FALSE}
wordcloud(words = complaints_narrative_corp_2$bigrams, freq = complaints_narrative_corp_2$n,
    max.words=200, random.order=FALSE, rot.per=0.35, 
    colors=brewer.pal(8, "Dark2"))
```
